---
title: "project3finished"
author: "Vincent Barletta"
date: "2023-05-17"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
install.packages("RSQLite",repos = "http://cran.us.r-project.org")
install.packages("DBI", repos = "http://cran.us.r-project.org")
install.packages("tidyverse", repos = "http://cran.us.r-project.org")
library(RSQLite)
library(DBI)
library(tidyverse)
```

```{r}
db = dbConnect(SQLite(), "stats.stackexchange.db")
dbListTables(db)
```

I would like to preface this by saying I have submitted this as an HTML document
only because I was having LaTeX issues with outputting as a PDF.

 Question 1

1.  How many users are there?

For this question, we will simply count the number of distinct IDs from
the user table. Typically, databases will have one-to-one correspondence
between Id and User accounts. We first will check to make sure that
there is not two of the same ID in the database; this shouldn't occur
since it is the primary key, but it is good practice to check.

```{r}

dbGetQuery(db, "SELECT Id, COUNT(*) FROM Users GROUP BY Id HAVING COUNT(*) > 1")
print("This gives no rows, meaning there are no IDs that occur twice in the table.")

dbGetQuery(db, "SELECT COUNT(Distinct Id) FROM Users")

```

There are 321677 unique users registered on the stats stack exchange
website.

 Question 2

2.  How many users joined since 2020? (Hint: Convert the CreationDate to
    a year.)

```{r}
dbGetQuery(db, "SELECT COUNT(Distinct Id) FROM Users
           WHERE CAST(CreationDate AS DATE) >= 2020")

```

100,796 new users have joined since 2020. We simply cast the
CreationDate as DATE and only collect records when the year is \>= 2020.

 Question 3

3.  How many users joined each year? Describe this with a plot,
    commenting on any anomalies.

```{r}
joined_distribution <- dbGetQuery(db, "SELECT CAST(CreationDate AS DATE) as Year, COUNT(Distinct Id) as Users FROM Users GROUP BY CAST(CreationDate AS DATE)")

ggplot(joined_distribution, aes(x = Year, y = Users)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Distribution of Users Joined Each Year",
       x = "Year", y = "Number of Users")

```

Here, we can see that 2017 is the peak of all users joining. The
distribution grows exponentially from the website's creation date in
2010 up until 2017 before steadily decreasing after. 2023 has very few
entries as the year is still not finished.

 Question 4

4.  How many different types of posts are there in the Posts table? Get
    the description of the types from the PostTypeIdMap table. In other
    words, create a table with the description of each post type and the
    number of posts of that type, and arrange it from most to least
    occurrences.

```{r}

post_types <- dbGetQuery(db, "SELECT DISTINCT(PostTypeId) as PostTypeId, i.value as PostTypeName, COUNT(*) FROM Posts as p, PostTypeIdMap as i where i.id = p.PostTypeId GROUP BY PostTypeId ORDER BY COUNT(*) DESC")

post_types

```

Noticeably, there are no posts with PostTypeID = 8, the privilege wiki.
According to stackexchange's metadata description, these posts are,
"questions asking us to recommend or find a tool, library or favorite
off-site resource are off-topic for Stack Overflow as they tend to
attract opinionated answers and spam. Instead, describe the problem and
what has been done so far to solve it."

 Question 5

5.  How many posted questions are there?

We can use our table that we created for Question 4. Since Question is
the most common Post type, we just take the top result from this table.

```{r}

post_types[1,]

```

There are 204,370 posted questions.

 Question 6

6.  What are the top 50 most common tags on questions? For each of the
    top 50 tags on questions, how many questions are there for each tag.

```{r}
top50tags <-dbGetQuery(db, "SELECT Tag, COUNT(*) as Count FROM TagPosts GROUP BY Tag ORDER BY COUNT(*) DESC LIMIT 50")
head(top50tags)
tail(top50tags)
top_10_tags = head(top50tags, n = 10)

ggplot(top_10_tags, aes(x = reorder(Tag, -Count), y = Count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Distribution of Most Commonly Used Tags",
       x = "Tag Name", y = "Number of Posts with Tag") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 


```

Here, we group each tag by name and calculate how many appearances there
are of each tag across all questions. The 'R' tag has by far the most
appearances, with 28495 questions. Regression is not far behind with
28146 appearances. The rest of the top 6 are machine-learning,
time-series, probability, and hypothesis-testing. The 45th to 50th
ranked tags are modeling, references, multivariate-analysis,
econometrics, interaction, and linear-model.

7.  How many tags are in most questions?

```{r}
dbSendStatement(db, "CREATE VIEW tag_count10 as SELECT Id, COUNT(Tag) as Count FROM TagPosts GROUP BY Id")

tag_freq <- dbGetQuery(db, "SELECT Count, COUNT(Count) as Frequency FROM tag_count10 GROUP BY Count ORDER BY COUNT(Count) DESC")
tag_freq

```

Most questions have three tags. A question cannot have more than 5 tags,
and has to have at least one tag. 90.1% of questions have at least two
tags.

8.  How many answers are there?

```{r}

post_types[2,]

```

According to the post_types table we created for Question 4, any post
flagged with PostTypeId = 2 is an answer. By counting these posts, we
see that there are 197,928 Answers posted.

9.  What's the most recent question (by date-time) in the Posts table? •
    Find it on the stats.exchange.com Web site and provide the URL. •
    How would we map a question in the Posts table to the corresponding
    SO URL?

While we could go through the trouble of converting the CreationDate
variable into a Date, an easier shortcut is to simply order by the Post
Id in descending order, as the last ID will be the most recent post.

```{r}
dbGetQuery(db, "SELECT * FROM Posts WHERE PostTypeId = 1 ORDER BY Id DESC LIMIT 1")


```

I went onto stats exchange and looked up the user's profile by Id,
382402, and found the post on their profile. The url is:
<https://stats.stackexchange.com/questions/608458/are-there-any-methods-that-combine-mcmc-and-vi>

Questions in the post table follow a relatively simple URL pattern; we
simply just need to append the Id field onto the basic URL:
stats.stackexchange.com. We do not even need the post title to fully
load the page - which is helpful since we would have to replace spaces
with '-' and decapitalize all characters.

10. For the 10 users who posted the most questions • How many questions
    did they post? • What are the users' names? • When did they join SO?
    • What is their Reputation? • What country do they have in their
    profile?

We will connect the User and Posts table here. First, we will go into
the Posts table and group by OwnerUserId and count how many Ids there
are (questions posted). Then, we will connect the Users based on this
OwnerUserId.

```{r}

users_top_questions <-dbGetQuery(db, "SELECT OwnerUserId, COUNT(Id) as Count FROM Posts WHERE PostTypeId = 1 GROUP BY OwnerUserId ORDER BY COUNT(Id) DESC LIMIT 11")
users_top_questions = users_top_questions[-1,]
users_top_questions

dbWriteTable(db, "users_questions", users_top_questions, overwrite = TRUE)

dbGetQuery(db, "SELECT * FROM Users where ID = 77179")
top_user_info <- dbGetQuery(db, "SELECT u.Id, uq.Count, u.Reputation, u.CreationDate, u.DisplayName, u.Location FROM users_questions uq, Users u WHERE uq.OwnerUserId = u.Id")
top_user_info
dbWriteTable(db, "top_user_info", top_user_info, overwrite = TRUE)



```

The most populous result, by a large margin, is ' ', indicating deleted
user accounts (according to the main schema webpage). Therefore, we will
ignore them. We are left with 10 users with the most posted questions.
Interestingly, our number one result has a Reputation of 1 despite
posting the most questions. I looked up his profile, and he actually has
a reputation of 7,110, therefore leaving me wondering why this
particular piece of data is incorrect.

11. Following from the previous questions, for the 10 users who posted
    the most questions, how many gold, silver and bronze badges does
    each of these 10 individuals have?

```{r}
medal_counts <- dbGetQuery(db, "SELECT Id, DisplayName, MedalName, COUNT(Medal) as Count
                FROM (SELECT t.Id, t.DisplayName, b.Class as Medal, bc.value as MedalName 
                From top_user_info t 
                LEFT JOIN Badges b 
                on t.Id = b.UserId 
                INNER JOIN BadgeClassMap bc
                on b.Class = bc.id)
                GROUP BY Id, DisplayName, Medal
                ")

dbWriteTable(db, "medal_counts", medal_counts, overwrite = TRUE)

dbGetQuery(db,"SELECT Id, DisplayName,
  MAX(CASE WHEN MedalName = 'Gold' THEN Count END) AS Gold,
  MAX(CASE WHEN MedalName = 'Silver' THEN Count END) AS Silver,
  MAX(CASE WHEN MedalName = 'Bronze' THEN Count END) AS Bronze
  FROM medal_counts
  GROUP BY Id, DisplayName")



```

15. What question has the most comments associated with it? • how many
    answers are there for this question?

```{r}

dbGetQuery(db, "SELECT MAX(CommentCount), Id, Title, AnswerCount FROM Posts WHERE PostTypeId = 1")

```

The question with the most comments is QuestionId = 328630, a question
titled: "Is ridge regression useless in high dimensions (n≪p)? How can
OLS fail to overfit?" with a total of 54 comments. Surprisingly, it only
has 6 answers.

16. How many comments are there across all posts? • How many posts have
    a comment? • What is the distribution of comments per question?

```{r}

dbGetQuery(db, "SELECT SUM(CommentCount) FROM Posts")
dbGetQuery(db, "SELECT COUNT(Id) FROM Posts WHERE CommentCount > 0 and PostTypeId = 1")
dbGetQuery(db, "SELECT AVG(CommentCount) FROM Posts WHERE PostTypeId = 1")
comment_distribution <- dbGetQuery(db, "SELECT Id, CommentCount FROM Posts WHERE PostTypeId = 1 ORDER BY CommentCount DESC")


hist(comment_distribution$CommentCount, breaks = 50,
     main = "Distribution of CommentCounts",
     xlab = "CommentCounts", ylab = "Frequency")

dbGetQuery(db, "SELECT COUNT(Id) FROM Posts WHERE CommentCount > 0 and PostTypeId = 1")



```

There are a total of 768,069 comments across all Posts. There are
229,859 posts that have at least one comment.

On average, a question gets 2.171 comments. As we can see by our
histogram, a vast majority of the questions do not have any comments at
all. From our last query, we see that only 128,280 questions out of a
total 204,370 have comments, meaning that 37.2% of questions have no
comments at all.

## Required Questions

21. Compute the table that contains • the question, • the name of the
    user who posted it, • when that user joined, • their location • the
    date the question was first posted, • the accepted answer, • when
    the accepted answer was posted • the name of the user who provided
    the accepted answer.

Although it is more computationally expensive to do, I like to break up
questions like this into multiple parts. Since the Posts table contains
both the questions and the answers, I create two separate tables and
join them together for our final result.

The first table that we create combines Question info with the user who
posted the question's account information. The second table combines the
Answer info with the user who posted the answer's account information.

Lastly, we use a left join to combine the two tables. It is important to
note that this returns all of matches that our question table has with
the answer table. Therefore, any questions that do not have an accepted
answer are left out of this table. This question was left ambiguous as
to if we wanted to include questions without an accepted answer, so we
will work with the interpretation that we only want questions with
accepted answers in this table.

There are 201,001 questions posted by non-deleted users, and 66,213 have
accepted answers.

```{r}

question_info <- dbGetQuery(db, "SELECT p.Id as QuestionID, p.Title as QuestionTitle, u.DisplayName as Username, u.Location, p.CreationDate as QuestionPostedDate, u.CreationDate as UserJoinedDate, AcceptedAnswerId
           FROM Posts p, Users u 
           WHERE u.Id = p.OwnerUserId and
           p.PostTypeId = 1 
           ")
nrow(question_info)


answer_info <- dbGetQuery(db, "SELECT p.Id as AnswerID, p.Body as Answer, p.CreationDate as AnswerPostedDate, u.DisplayName as AnswerUsername
           FROM Posts p, Users u
           WHERE u.Id = p.OwnerUserId and
           p.PostTypeId = 2")

dbWriteTable(db, "question_info", question_info, overwrite = TRUE)
dbWriteTable(db, "answer_info", answer_info, overwrite = TRUE)

qna <- dbGetQuery(db, "SELECT q.QuestionTitle, q.Username, q.UserJoinedDate, q.Location, q.QuestionPostedDate,
          a.Answer, a.AnswerPostedDate, a.AnswerUsername
          FROM question_info q
          LEFT JOIN answer_info a
          WHERE AcceptedAnswerId = AnswerID
          ")
head(qna, n = 1)
nrow(qna)

```

22. Determine the users that have only posted questions and never
    answered a question? (Compute the table containing the number of
    questions, number of answers and the user's login name for this
    group.) How many are there?

My philosophy: go to Posts table, group by OwnerUserId and count the
total number of posts by PostType = 1. Then, we will do the same by
PostType = 2. Then, we will look for User IDs that are in the first
table, but are NOT in the second table. Lastly, we will do an inner join
with the user table to get their login name; by doing this, we also
filter out the deleted users with blank user IDs as they do not have an
associated username.

From this, we find out that there are 76,410 users that have posted a
question that have not answered a question.

```{r}

question_count <- dbGetQuery(db, "SELECT OwnerUserId, COUNT(*) as QuestionCount FROM Posts WHERE PostTypeId = 1 GROUP BY OwnerUserId  ORDER BY COUNT(*) DESC ")

answer_count <- dbGetQuery(db, "SELECT OwnerUserId, COUNT(*) as AnswerCount FROM Posts WHERE PostTypeId = 2 GROUP BY OwnerUserId  ORDER BY COUNT(*) DESC ")

dbWriteTable(db, "question_count", question_count, overwrite = TRUE)
dbWriteTable(db, "answer_count", answer_count, overwrite = TRUE)

q22_final <- (dbGetQuery(db, "SELECT q.OwnerUserId, q.QuestionCount, u.DisplayName
  FROM question_count q
  LEFT JOIN answer_count a ON q.OwnerUserId = a.OwnerUserId
  INNER JOIN Users u ON q.OwnerUserId = u.Id
  WHERE a.OwnerUserId IS NULL"))
head(q22_final)
nrow(q22_final)

```

23. Compute the table with information for the 75 users with the most
    accepted answers. This table should include • the user's display
    name, • creation date, • location, • the number of badges they have
    won, -- the names of the badges (as a single string) • the dates of
    the earliest and most recent accepted answer (as two fields) -- the
    (unique) tags for all the questions for which they had the accepted
    answer (as a single string)

This question was super difficult! It really tested the bounds of my
knowledge. While I initially thought I could do much of this problem in
one go, I had to go back to my previous method of breaking it up into
chunks.

I went head-on into this problem simply using the answer_count table at
first. However, I realized around halfway into this question that I did
not implement a method to check that the answer was an accepted answer.
The solution that I decided on involved matching the Id of the answer
Post to the AcceptedAnswerId of the question by using the ParentId. The
ParentId provides the question that the answer solves, so we do a
subquery to find the AAI when for matches between Id and ParentId. This
gives us our primary table, accepted_answer_count.

The first variables are fairly standard. We use GROUP_CONCAT for the
badge names as it was suggested on Piazza. For finding the dates, I used
ChatGPT to help with the conversion formula from String to Date. We use
this subquery method for ParentId here as well because it was at this
step that I realized we were not checking for accepted answers.

For the Distinct Tags, we used GROUP_CONCAT as before in conjunction
with our previous methods. We connect our answers to their associated
question's tags using the Parent Tag as before.

My final output will only show one row because each row has a lot of tags and 
badge names.

```{r}

accepted_answer_count <- dbGetQuery(db, "SELECT p.OwnerUserId, COUNT(*) as AnswerCount FROM Posts p
                          WHERE p.PostTypeId = 2 and p.Id = 
                          (SELECT AcceptedAnswerId from Posts WHERE Id = p.ParentId)
                           GROUP BY OwnerUserId  
                           ORDER BY COUNT(*) DESC ")

dbWriteTable(db, "accepted_answer_count", accepted_answer_count, overwrite = TRUE)

distinct_tags <- dbGetQuery(db, "SELECT p.OwnerUserId, GROUP_CONCAT(DISTINCT t.Tag) as DistinctTags  FROM Posts p
                          LEFT JOIN TagPosts t on p.ParentId = t.Id
                          WHERE p.PostTypeId = 2 and p.Id = 
                          (SELECT AcceptedAnswerId from Posts WHERE Id = p.ParentId)
                           GROUP BY OwnerUserId  
                           ORDER BY COUNT(*) DESC ")

dbWriteTable(db, "distinct_tags", distinct_tags, overwrite = TRUE)


intermediary <- dbGetQuery(db, "SELECT a.OwnerUserId, a.AnswerCount, u.DisplayName, u.CreationDate, u.Location, COUNT(b.Class) as BadgeCount, GROUP_CONCAT(DISTINCT b.Name) as BadgeNames 
  FROM accepted_answer_count a
  LEFT JOIN Badges b on a.OwnerUserId = b.UserId
  INNER JOIN Users u ON a.OwnerUserId = u.Id
  GROUP BY OwnerUserId, DisplayName
  ORDER BY AnswerCount DESC")

dbWriteTable(db, "intermediary", intermediary, overwrite = TRUE)


#Conversion format provided to me via ChatGPT; I did not know how to convert it to a date without it simply converting the year (as I did in one of the earlier questions).

creationdates <- dbGetQuery(db, "SELECT u.OwnerUserId,
       MIN(strftime('%Y-%m-%d %H:%M:%S', p.CreationDate)) AS FirstPostDate,
       MAX(strftime('%Y-%m-%d %H:%M:%S', p.CreationDate)) AS LastPostDate
FROM accepted_answer_count u
LEFT JOIN Posts p ON u.OwnerUserId = p.OwnerUserId
WHERE PostTypeId = 2 and p.Id = (SELECT AcceptedAnswerId from Posts
                                WHERE Id = p.ParentId)
GROUP BY u.OwnerUserId
ORDER BY u.AnswerCount DESC")

dbWriteTable(db, "creationdates", creationdates, overwrite = TRUE)


head(dbGetQuery(db, "SELECT i.*, c.FirstPostDate, c.LastPostDate, d.DistinctTags
           FROM intermediary i, creationdates c, distinct_tags d
           WHERE i.OwnerUserId = c.OwnerUserId and i.OwnerUserId = d.OwnerUserId
           ORDER BY i.AnswerCount DESC
           LIMIT 75"), n = 1)

```



24. How many questions received no answers (accepted or unaccepted)? How
    many questions had no accepted answer?

From number 21, there are 201,001 questions posted by non-deleted users,
and 66,213 have accepted answers posted by non-deleted users.

According to this calculation, 134,788 questions do not have an accepted
answer. If we do a direct computation (as we do below), we find that
136,365 questions do not have an accepted answer. We will use the latter
number as some data may have been lost in the joining process of the
previous calculation.

In order to find the questions with no answer at all, we will look for
matches between Question Id's and the Parent Id's of answers. If there
are Question IDs that do not have any matching Parent IDs, then that
question has no unaccepted answers.

```{r}

dbGetQuery(db, "SELECT COUNT(Id) FROM Posts
           WHERE PostTypeId = 1 AND AcceptedAnswerId = ''
           AND Id != '' ")


 dbGetQuery(db, "SELECT COUNT(Id) FROM Posts 
              WHERE PostTypeId = 1 AND
              Id NOT IN (
                SELECT ParentId FROM Posts
              )
            ")

```

There are 66,970 questions that do not have any answers. Alternatively,
we can also just count posts where AnswerCount = 0.

```{r}

 dbGetQuery(db, "SELECT COUNT(Id) FROM Posts 
              WHERE PostTypeId = 1 AND
              AnswerCount = 0
            ")

```

25. What is the distribution of answers per posted question?

From the last question, we already know that there are many questions
that are left unanswered. However, many intriguing posts also garner
multiple answers. Therefore, the average number of answers across all
posts is just under 1 at 0.9684787.

There is one question that got 153 different answers. I was intrigued,
and I found that it was a post asking for people's favorite statistic's
quotes.

If we convert our AnswerCount into a table, we can clearly see the
distribution laid out. The vast majority are at the frontend of the
distribution, with either 0, 1, or 2 answers. We use a log-adjust graph
in order to visibly display all of our data on one graph. It is very
important to make note of the y-axis as it changes dramatically over a
small distance. We can see that the first three entries that go above
the last bar are well above 10,000, and the second bar is very close to
reaching 100,000.

In comparison, the next most frequent value, 3 answers, occurs only
7,246 across all posts. This quickly decreases to 2408, 905, 401, 210,
136, 82, and finally only 62 occurences of a post receiving 10 answers.

```{r}

answer_distribution <- dbGetQuery(db, "SELECT Id, AnswerCount FROM Posts 
              WHERE PostTypeId = 1 
              ORDER BY AnswerCount DESC
            ")

dbGetQuery(db, "SELECT AVG(AnswerCount) FROM Posts WHERE PostTypeId = 1")


counts <- table(answer_distribution$AnswerCount)
counts
barplot(counts, log = "y", col = "steelblue", main = "Distribution of Answer Count",
        xlab = "AnswerCounts", ylab = "Frequency (log scale)")


```

26. What is the length of time for a question to receive an answer? to
    obtaining an accepted answer?

First, we create tables with the times for Question creation date and
answer creation date and join them together based on ParentId and
Question ID.

In the full table that we create, we have multiple answers submitted for
each question. We want only the first response for each question. After
scavenging through StackOverFlow, I found that we can achieve this via
partitioning by order of AnswerPosted. This ranks each possible
response. We then can select only the first row.

We find the difference between each time in seconds, and divide by 60 to
get the difference in minutes in between question posting and the first
answer being posted.

To get the first accepted answer, it is a bit easier. We simply find the
entry where the AcceptedAnswerId matches one of the Answer IDs, and
compute the difference similarly.

```{r}

q_time <- dbGetQuery(db, "SELECT Id as QId, AcceptedAnswerId, (strftime('%Y-%m-%d %H:%M:%S', p.CreationDate)) AS QuestionPosted
           FROM Posts p
           WHERE PostTypeId = 1")

a_time <- dbGetQuery(db, "SELECT p.Id as AId, p.ParentId, (strftime('%Y-%m-%d %H:%M:%S', p.CreationDate)) AS AnswerPosted
           FROM Posts p
           WHERE PostTypeId = 2
           ")

dbWriteTable(db, "q_time", q_time, overwrite = TRUE)
dbWriteTable(db, "a_time", a_time, overwrite = TRUE)

fullresults_qa <- dbGetQuery(db, "SELECT q.*, a.* FROM q_time q, a_time a
           WHERE a.ParentId = q.QId
           ")

dbWriteTable(db, "fullresults_qa", fullresults_qa, overwrite = TRUE)


first_answer <- dbGetQuery(db, "SELECT QId, AcceptedAnswerId, AId, (strftime('%s', AnswerPosted) - strftime('%s', QuestionPosted))/60 as MinutesUntilFirstAnswer
FROM (
    SELECT QId, AcceptedAnswerId, QuestionPosted, AId, ParentId, AnswerPosted,
           ROW_NUMBER() OVER (PARTITION BY QId ORDER BY AnswerPosted) AS rn
    FROM fullresults_qa
) AS sub WHERE rn = 1")

head(first_answer)

first_accepted <- dbGetQuery(db, "SELECT QId, AcceptedAnswerId, (strftime('%s', AnswerPosted) - strftime('%s', QuestionPosted))/60 as MinutesUntilAcceptedAnswer
           FROM fullresults_qa WHERE AId = AcceptedAnswerId")
head(first_accepted)



```

27. How many answers are typically received before the accepted answer?

Here, we will do a self join in order to calculate how many answers are
typically submitted for each question before the accepted answer is
received. We check for when AcceptedAnswerId != 0 as these questions do
not have an accepted answer. We want to find areas when t2.AI is NULL as
it when it does not equal the accepted answer. We subtract the Count by
1 as it always has an extra value.

We find that on average, a question has 0.263 answers submitted before
the submitted answer is provided. This means that typically, the first
answer is the accepted answer for most questions.

```{r}

numbefore <- dbGetQuery(db, "SELECT t1.QId, (COUNT(*)-1) AS NumRowsBeforeAccepted
FROM fullresults_qa t1
LEFT JOIN fullresults_qa t2 ON t1.QId = t2.QId AND t2.AId = t1.AcceptedAnswerId
WHERE (t2.AId IS NULL OR t2.AId > t1.AId) AND t1.AcceptedAnswerId != 0
GROUP BY t1.QId;")

dbWriteTable(db, "numbefore", numbefore, overwrite = TRUE)
dbGetQuery(db, "SELECT AVG(NumRowsBeforeAccepted) FROM numbefore")

```
